Resurgence of the Airy function

### 2022-01-12 airy-resurgence.tex
Add notes from 10 Jan conversation

It happens\footnote{How to verify this? This hypergeometric function can be written in terms of Legendre functions, but I don't know where to go from there.} that for our desired branch of $u$,
\[ \frac{1}{4u^2 - 1} = F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
so we can rewrite integral~\ref{integral:mod-bessel-zeta} as
\[ K(z) = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we'll follow below.

@@

The quadratic transformation identity 15.8.27 from \cite{dlmf} shows that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
\begin{align*}
F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) & = \tfrac{1}{3}(\hat{g}_1 + \hat{g}_0) \\
& = \tfrac{1}{2\sqrt{3}}(\hat{f}_1 + \hat{f}_0)
\end{align*}
so we have
\[ K(z) = \frac{1}{6i} \int_{\gamma_z} e^{-z\zeta} (\hat{f}_1 + \hat{f}_0)\;d\zeta. \]
The solution $\hat{f}_1$ is regular on $\zeta \in [1, \infty)$, so it integrates to zero. The solution $\hat{f}_0$ looks like $(1 - \zeta)^{-1/2}$ times a function which is regular on $\zeta \in [1, \infty)$, so integrating it along $\gamma_z$ is the same as integrating it negative-twice along the contour that goes rightward from $1$, with its value continued from above the singularity. Hence,
\begin{align*}
K(z) & = \frac{i}{3} \int^\infty_1 e^{-z\zeta} \hat{f}_0\;d\zeta \\
& = \tfrac{i}{3} \laplace_{\zeta_1} \hat{f}_0.
\end{align*}
\textbf{[Constant conflicts with Section~\ref{spatial}]}
\subsection{Correspondence with Mari\~{n}o's series}
Let $f_1(z)$ be the holomorphic function corresponding to Mari\~{n}o's formal power series $\varphi_1(z^{-1})$. The formal power series corresponding to $f$ will be written in the variable $z$.

>>>>

It happens\footnote{How to verify this? This hypergeometric function can be written in terms of Legendre functions, but I don't know where to go from there. \textbf{Veronica:} Look at ``Special cases'' section in \cite{dlmf}, e.g. 15.4.14!} that for our desired branch of $u$,
\[ \frac{1}{4u^2 - 1} = F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
so we can rewrite integral~\ref{integral:mod-bessel-zeta} as
\[ K(z) = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we'll follow below.

@@

The quadratic transformation identity 15.8.27 from \cite{dlmf} shows \textbf{[verified numerically]} that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
\begin{align*}
F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) & = \tfrac{1}{3}(\hat{g}_1 + \hat{g}_0) \\
& = \tfrac{1}{2\sqrt{3}}(\hat{f}_1 + \hat{f}_0)
\end{align*}
so we have
\[ K(z) = \frac{1}{6i} \int_{\gamma_z} e^{-z\zeta} (\hat{f}_1 + \hat{f}_0)\;d\zeta. \]
The solution $\hat{f}_1$ is regular on $\zeta \in [1, \infty)$, so it integrates to zero. The solution $\hat{f}_0$ looks like $(1 - \zeta)^{-1/2}$ times a function which is regular on $\zeta \in [1, \infty)$, so integrating it along $\gamma_z$ is the same as integrating it negative-twice along the contour that goes rightward from $1$, with its value continued from above the singularity. Hence,
\begin{align*}
K(z) & = \frac{i}{3} \int^\infty_1 e^{-z\zeta} \hat{f}_0\;d\zeta \\
& = \tfrac{i}{3} \laplace_{\zeta_1} \hat{f}_0.
\end{align*}
\textbf{[Constant conflicts with Section~\ref{spatial}]}
\subsection{Correspondence with Mari\~{n}o's series}
Let $f_1(z)$ be the holomorphic function corresponding to Mari\~{n}o's formal power series $\varphi_1(z^{-1})$. The formal power series corresponding to $f$ will be written in the variable $z$.
